Fast Neural Machine Translation Implementation

### 2018-05-18 wnmt.2018/wnmt.tex

The Amun engine implements an efficient batching algorithm that takes into account the actual number of hypotheses that need to be decoded at each decoding step, Figure~\ref{algo:Mini-batching}.

@@

Thirdly, the calculation of $max$ and $sum$ can be accomplished in one loop by adjusting $sum$ whenever a higher $max$ is found during the looping:
\begin{eqnarray*}
sum & = & e^{x_t - max_b} + \sum_{i=0...t-1}{e^{x_i - max_b}} \\
    & = & e^{x_t - max_b} + \sum_{i=0...t-1}{e^{x_i - max_a + \Delta}}  \\
    & = & e^{x_t - max_b} + e^{\Delta} \times \sum_{i=0...t-1}{e^{x_i - max_a}} 
\end{eqnarray*}
where $max_a$ is the previous
%!dtr! original as in the one at the start of this iteration, or original as the one at the start of the process? 
maximum value, $max_b$ is the now higher maximum value, i.e., $max_b > max_a$, and $\Delta = max_a - max_b$. The outline of our function is shown in Algorithm~\ref{algo:Fused Kernel}.

>>>>

Amun implements an efficient batching algorithm that takes into account the actual number of hypotheses that need to be decoded at each decoding step, Figure~\ref{algo:Mini-batching}.

@@

Thirdly, the calculation of $max$ and $sum$ can be accomplished in one loop by adjusting $sum$ whenever a higher $max$ is found during the looping:
\begin{eqnarray*}
sum & = & e^{x_t - max_b} + \sum_{i=0...t-1}{e^{x_i - max_b}} \\
    & = & e^{x_t - max_b} + \sum_{i=0...t-1}{e^{x_i - max_a + \Delta}}  \\
    & = & e^{x_t - max_b} + e^{\Delta} \times \sum_{i=0...t-1}{e^{x_i - max_a}} 
\end{eqnarray*}
where $max_a$ is the previous maximum value, $max_b$ is the now higher maximum value, i.e., $max_b > max_a$, and $\Delta = max_a - max_b$. The outline of our function is shown in Algorithm~\ref{algo:Fused Kernel}.
